%-------------------------------------------------------------------------------
%	SECTION TITLE
%-------------------------------------------------------------------------------
\cvsection{Experience}


%-------------------------------------------------------------------------------
%	CONTENT
%-------------------------------------------------------------------------------
\begin{cventries}
%---------------------------------------------------------
  \cventry
    {GSoC Student} % Job title
    {Google Inc.} % Organization
    {Mountain View, CA} % Location
    {May 2016 - Aug. 2016} % Date(s)
    {
      \begin{cvitems} % Description(s) of tasks/responsibilities
        \item {Worked on the Python library for GRPC - an open source RPC system.}
        \item {Studied different implementations of Python and how they differ from the reference implementation.}
        \item {Added Support for Python 3.x and PyPy for GRPC Python and ensured product stability over transition from Beta to General Availability.}
      \end{cvitems}
    }
%---------------------------------------------------------
  \cventry
    {Undergraduate guided research on Python integration for Rasdaman} % Job title
    {Large-Scale Scientific Information Systems Group} % Organization
    {Bremen, Germany} % Location
    {Sep. 2015 - May 2016} % Date(s)
    {
      \begin{cvitems} % Description(s) of tasks/responsibilities
        \item {Researched means of retrieving data from remote Rasdaman databases over RPC in a simple fashion.}
        \item {Implemented prototype that enables generation of RasQL queries from NumPy algorithms and client-side execution of arbitrary RasQL queries on the server.}
      \end{cvitems} 
    }
%---------------------------------------------------------
\cventry
  {Member} % Job title
  {Stanford Crowd Research Collective} % Organization
  {Stanford, CA} % Location
  {Dec. 2015 - May 2016} % Date(s)
  {
    \begin{cvitems} % Description(s) of tasks/responsibilities
      \item {Conducted research on an optimal solution for the microworking landscape along with a diverse research team around the globe.}
      \item {Contributed to the devops and features of a Django and Angular.js based web application in the research engineering team.}
    \end{cvitems} 
  }
%---------------------------------------------------------
\cventry
  {Teaching Assistant} % Job title
  {Jacobs University} % Organization
  {Bremen, Germany} % Location
  {Sep. 2015 - Jan. 2016} % Date(s)
  {
    \begin{cvitems} % Description(s) of tasks/responsibilities
      \item {Created and graded assignments and examinations, conducted code reviews, helped weak students grasp the coursework.}
    \end{cvitems} 
  }
%---------------------------------------------------------
  \cventry
    {Software Engineering Intern} % Job title
    {Dolby Laboratories Inc.} % Organization
    {Nuremberg, Germany} % Location
    {Mar. 2015 - Sep. 2015} % Date(s)
    {
      \begin{cvitems} % Description(s) of tasks/responsibilities
        \item {Worked on a data visualization heavy web application to visualize performance metrics over a variety of hardware for each commit in a project.}
        \item {Architected and developed the architecture for a customizable visualization dashboard using D3.js and Angular.js}
        \item {Lead to company wide adoption of the product enabling project managers to keep track of their project growth on a continuous basis.}
      \end{cvitems}
    }

%---------------------------------------------------------
\end{cventries}
